Dewlap color variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies

### 2021-12-20 ms/sections/discussion.tex
stuff

Detectable differences in dewlap color between populations are surprising, as habitats were often in close geographical proximity to each other (as close as a few hundred meters on Bimini and most of the time within ten kilometers)\sout{. Indeed, given that (1) the populations were continuously distributed between the habitats, (2) populations from different habitats were not monophyletic with respect to mitochondrial haplotypes (\citealt{vandeSchoot2016} unpublished thesis), and (3) \textit{A. sagrei} is highly mobile \citep{Kamath2018}, we would have expected more homogeneous distributions of color phenotypes within islands due to gene flow, with fewer differences between populations, especially those in close proximity.} \textcolor{olive}{, and we would have expected gene flow to cause a more homogeneous distriution of color phenotypes within islands. While little is known about the cruising range of individuals from our study populations (but see \citealt{Kamath2018, Steinberg2017}), \textit{A. sagrei} are polygynandrous (where both males and females mate with multiple mates, \citealt{Kamath2018,Kamath2018a}), thus offering opportunity for gene flow, especially given that lizards were distributed continuously and at high densities within the islands we sampled. Consistent with that, while populations from different islands were monophyletic, individuals within islands were not monophyletic with respect to habitat based on mitochondrial haplotypes (\citealt{vandeSchoot2016} unpublished thesis).}\\

>>>>

Detectable differences in dewlap color between populations are surprising, as habitats were often in close geographical proximity to each other (as close as a few hundred meters on Bimini and most of the time within ten kilometers)\textcolor{red}{. Indeed, given that (1) the populations were continuously distributed between the habitats, (2) populations from different habitats were not monophyletic with respect to mitochondrial haplotypes (\citealt{vandeSchoot2016} unpublished thesis), and (3) \textit{A. sagrei} is highly mobile \citep{Kamath2018}, we would have expected more homogeneous distributions of color phenotypes within islands due to gene flow, with fewer differences between populations, especially those in close proximity.} \textcolor{olive}{, and we would have expected gene flow to cause a more homogeneous distriution of color phenotypes within islands. While little is known about the cruising range of individuals from our study populations (but see \citealt{Steinberg2017, Kamath2018}), \textit{A. sagrei} are polygynandrous (where both males and females mate with multiple mates, \citealt{Kamath2017, Kamath2018, Kamath2018a}), thus offering opportunity for gene flow, especially given that lizards were distributed continuously and at high densities within the islands we sampled. Consistent with that, while populations from different islands were monophyletic, individuals within islands were not monophyletic with respect to habitat based on mitochondrial haplotypes (\citealt{vandeSchoot2016} unpublished thesis).}\\
